Hidden Talents Multiverse Analysis

### 2021-06-27 README.Rmd
Fix typo in README
manually merge changes

The names of each folder are intended to be self-explanatory. There are five top-level folders to organize the inputs and outputs of this project:

1.  `codebooks/`: lists of variable names, labels, and value labels (where applicable).
2.  `data/`: data, stored as an `.Rdata` file and `.csv` files.
3.  `figures/`: all figures that are produced by R-scripts
4.  `multiverse-objects/`: all `.Rdata` files containing objects necessary for performing multiverse analyses and storing intermediary results

@@

```{r}
fs::dir_tree(".", regexp = "^README|.Rproj$", invert = T)
```

@@

## Figures

These are all figures that are produced by R-scripts. They are divided into the following categories:

-   Primary analysis figures

-   Secondary analysis figures

    -   Set 1
    -   Set 2

@@

-   `0-functions/`: custom R-functions written for this project
-   `1-data-prep/`: Data processing scripts
-   `2-primary-analyses/`: Primary analysis scripts
-   `3-secondary-analyses/`: Secondary analysis scripts

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = T) %>% 
  as_raw_html()
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>% 
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = T) %>% 
  as_raw_html()
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>% 
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = T) %>% 
  as_raw_html()
```

>>>>

The names of each folder are intended to be self-explanatory. There are six top-level folders to organize the inputs and outputs of this project:

1.  `codebooks/`: lists of variable names, labels, and value labels (where applicable).
2.  `data/`: data, stored as an `.Rdata` file and `.csv` files.
3.  `manuscript`: a manuscript written in R markdown for submission to a journal.
4.  `multiverse-objects/`: all `.Rdata` files containing objects necessary for performing multiverse analyses and storing intermediary results.
5.  `scripts/`: R-scripts that read, analyze, and produce all multiverse objects.
6.  `supplement/`: a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.

@@

```{r}
fs::dir_tree(".", regexp = "^README|.Rproj$|log$|tex$|_files|resources", invert = T)
```

@@

## Manuscript

This directory contains the manuscript for this project. It was written in R Markdown and is 100% reproducible. The `.Rmd` fie contains the written text with all figures, tables, and in-text statistics. All outputs reported in the manuscript were staged prior to compiling into a `.pdf` document and stored in a `.Rdata` file called `staged-objects.Rdata`. The R Markdown document reads these staged files to make the overall document easier to read. The scripts that produce the staged objects are located in the `manuscript/scripts/` directory and are named to be self-explanatory. The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the manuscript.

@@

-   `0-functions/`: Custom R-functions written for this project
-   `1-data-prep/`: Data processing scripts
-   `2-primary-analyses/`: Primary analysis scripts
-   `3-secondary-analyses/`: Secondary analysis scripts

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything()) %>% 
  as_raw_html()
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything()) %>% 
  as_raw_html()
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything()) %>% 
  as_raw_html()
```

## Supplement

This directory contains the supplement to the manuscript described above. The supplement was produced using the same approach as the manuscript: it was written in R Markdown, is 100% reproducible, and all outputs were staged prior to compiling into a `.pdf`. The staged objects are stored in `supplement/staged-objects.Rdata`. The scripts that produce the staged objects are located in the `supplement/scripts/` directory and are named to be self-explanatory. The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the supplement.
